### 2021-04-22 architecture.tex
Modify a diagram to make it shorter

{ rank = same;
Problem [label="Problem P"];
pi [label=<Precedence &pi;>];
rho [label=<Precedence &rho;>];
}

Graphifier [style=rounded, label="Graph constructor"];
g [label="Graph"];
GCN [style=<rounded,bold>, label="GCN"];
SymbolEmbedding [label="Symbol embeddings"];
SymbolCostModel [style=<rounded,bold>, label="Output layer"];
SymbolCost [label="Symbol costs"];

{ rank = same;
Sort [style=rounded, label="Sort"];
LossFunction [style=rounded, label="Loss function"];
}

>>>>

{ rank = same;
pi [label=<Precedence &pi;>];
rho [label=<Precedence &rho;>];
}

Problem [label="Problem P"];

{ rank = same;
Graphifier [style=rounded, label="Graph constructor"];
g [label="Graph"];
GCN [style=<rounded,bold>, label="GCN"];
SymbolEmbedding [label="Symbol embeddings"];
SymbolCostModel [style=<rounded,bold>, label="Output layer"];
}

SymbolCost [label="Symbol costs"];

Sort [style=rounded, label="Sort"];
LossFunction [style=rounded, label="Loss function"];
